R for Clinical Study Reports and Submission

### 2021-11-19 tlf-efficacy-km.Rmd
update tlf-efficacy-km.Rmd
- update file format
automate rtf to pdf conversion
improve output figure details

```{r, out.width = "100%", out.height = "450px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/fig_km.png")
```

@@

```{r}
sum_fit <- summary(coxph(Surv(AVAL, 1-CNSR) ~ ARM  + strata(STRATAP), data = adtte_efs))
```

```{r}
fig_km <- ggsurvplot(
  fit,
  xlab = "Time in Months",
  ylab = "Survival Probability",
  break.time.by = 30.4367,
  xscale = "d_m",
  xlim = c(0, 200),
  linetype = c(1, 2, 3),
  risk.table = TRUE,
  risk.table.height = 0.3, # Useful when you have multiple groups
  legend = c(0.8, 0.9), legend.title = "",
  legend.labs = sort(unique(adtte_ttde$TRTP)),
  censor.size = 4,
  size = 0.8,
  title = "",
  censor.shape = "|",
  pval = TRUE,
  pval.method = TRUE,
  pval.coord = c(0, 0.1),
  pval.method.coord = c(0, 0.2),
  pval.size = 5,
  ggtheme = theme_classic2(base_family = "Times New Roman", base_size = 18)
)
```

@@

```{r}
# Save as PNG file
ggsave("tlf/fig_km.png", plot = print(fig_km, newpage = FALSE), width = 10, height = 6)

@@

>>>>

@@

```{r}
fig_km <- ggsurvplot(
  fit,
  xlab = "Time in Months",
  ylab = "Survival Probability",
  break.time.by = 30.4367,
  xscale = "d_m",
  xlim = c(0, 200),
  linetype = c(1, 2, 3),
  risk.table = TRUE,
  risk.table.height = 0.3, # Useful when you have multiple groups
  legend = c(0.8, 0.9), legend.title = "",
  legend.labs = sort(unique(adtte_ttde$TRTP)),
  censor.size = 4,
  size = 0.8,
  title = "",
  censor.shape = "|",
  pval = TRUE,
  pval.method = TRUE,
  pval.coord = c(0, 0.1),
  pval.method.coord = c(0, 0.2),
  pval.size = 5,
  font.family = "Times New Roman",
  ggtheme = theme_classic2(base_family = "Times New Roman", base_size = 18)
)
```

@@

```{r}
# Save as PNG file
grid.draw.ggsurvplot <- function(x) survminer:::print.ggsurvplot(x, newpage = FALSE)
ggsave("tlf/fig_km.png", plot = fig_km, width = 10, height = 6)

@@

```{r, include=FALSE}
rtf2pdf("tlf/fig_km.rtf")
```
